Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-16 paper.tex
Be explicit about wake recovery Re

In the near-wake of the turbine we observed lower levels of turbulence with
increasing Reynolds number, along with lower levels of turbulent transport with
respect to mean streamwise momentum and mean kinetic energy recovery in the
streamwise direction. Vertical advection---the largest transport mechanism
measured---showed little $Re$-dependence, whereas the negative effects of
cross-stream advection was enhanced at high $Re$, which may be due to larger
free surface deformation reducing the near-wake's cross-sectional area. Despite
being order of magnitude smaller than other transport processes, viscous
diffusion increased rapidly with decreasing $Re$, and is expected to become
significant to the wake dynamics around $Re_D \sim 10^4$. Overall, the total
wake transport measured leveled off at essentially the same Reynolds number that
the performance did.

>>>>

In the near-wake of the turbine we observed lower levels of turbulence with
increasing Reynolds number, along with lower levels of turbulent transport with
respect to mean streamwise momentum and mean kinetic energy recovery in the
streamwise direction. Vertical advection---the largest transport mechanism
measured---showed little $Re$-dependence, whereas the negative effects of
cross-stream advection were enhanced at high $Re$, which may be due to larger
free surface deformation reducing the near-wake's cross-sectional area. Despite
being orders of magnitude smaller than other transport processes, viscous
diffusion increased rapidly with decreasing $Re$, and is expected to become
significant to the wake dynamics around $Re_D \sim 10^4$. Overall, the total
wake transport measured leveled off at essentially the same Reynolds number that
the performance did---$Re_D \approx 0.8 \time 10^6$.
